\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
remove the 2nd tranformations

For presentation purposes, we provide a sketch of a highly simplified language
for describing reducers. The language allows us to give examples of reducers and
to discuss our approach for checking their commutativity. Let $\Var$ be a set of
\emph{integer variables}. An \emph{integer expression} in $\Exp$ can either be
a~variable from $\Var$, a constant value, a call to the $\cur$ function that
reads and consumes an input value of the reducer, their combinations over basic
arithmetic operations, or a non-deterministically chosen integer value $*$. A
\emph{command} in $\Cmd$ can be an assignment, a branch statement, a sequence of
commands, or an $out(v)$ statement that outputs the value of $v \in \Var$. A
\emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$ where $s_1,s_2,s_3
\in \Cmd$. According to our observation over hundreds  of reducer programs in
open repositories, reducer programs are almost always in this form. The
$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until
the entire input list is consumed. An example of a reducer is shown in
Figure~\ref{fig:reducer_example}.

@@

The \emph{Preprocessor component} first compiles a reducer program to bytecode
and uses the tool Soot to further convert it to the so-called ``Jimple'' format,
which is an intermediate language designed to simplify the analysis of Java
programs. Under the Hadoop MapReduce framework, the permutation of the input is
handled by the scheduler/shuffler component and is affected by issues like
network latency, which are not controllable by programmers. In order to deal
with such issues, we wrote our own dummy Hadoop environment for the reducer as a
part of the Preprocessor component so that the input order of the reducer is now
controlled by J-ReCoVer. Finally, the Preprocessor performs some program
transformation tasks to simplify the analysis. For example, it converts all
output commands $out(e)$ inside loops to a special assignment (as explained in
Section~\ref{sec:program_trans1}).

@@

Before entering the Prover component, the Preprocessor first performs two
program transformations to simplify the verification task
(Section~\ref{sec:program_trans1}). The output of the preprocessor is a
commutativity-equivalent reducer program. The algorithm of the Prover is then
explained in Section~\ref{sec:prover}.

%=============================================================================
\vspace*{-2mm}
\subsection{The Program Transformations in the Preprocessor}
\label{sec:program_trans1}
\vspace*{-1mm}
%=============================================================================

%-----------------------------------------------------------------------------
\paragraph*{Handling the access to $\cur$ before entering the loop.}
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
\paragraph*{Handling output inside the loop body} 
%-----------------------------------------------------------------------------

Another problem for our reduction to SMT is the fact that the reducer program
can perform the output command $out(e)$ inside the loop body $s_2$. Since our
SMT-based commutativity checking presented later on will be based on examining
possible values of the variables that appear in the $s_2$ loop body only (these
values then determine the output performed in $s_3$), we will replace each such
$out(e)$ command by the assignment $v:=e$ for a fresh variable $v$. This makes
the value that will be output visible for our analysis. The fact that we loose
the output command does not matter since---as already said---we will not track
the output commands but values of the variables that determine the value of the
output.  Notice that the value of $v$ stays the same from the point it has been
assigned a value until the end of the loop body $s_2$. If the value that $v$ can
have at the end of $s_2$ does not change for any permutation of the input lists,
we know that the reducer is commutative wrt all output values produced inside
the loop body $s_2$.

@@

After the transformations described above, the reducer $s_1;\rloop\{s_2\};s_3$
never calls the $\cur$ function in the $s_1$ part before entering the loop and
never outputs values inside the loop body (the $s_2$ part). The command $s_2$
can be viewed as a function $F$ that reads the values of all variables and the
current input before executing $s_2$ and outputs the values of all variables
after $s_2$. Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
\rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$ where $n$ is
the current input value of the reducer, $x_i$ and $x_i'$ are the values of the
variables before and after the execution of $s_2$, respectively, for
$i\in[1,k]$. The construction of $F$ from $s_2$ can be done in the standard way.

@@

\begin{wraptable}{r}{4cm}
	\vspace{-0.7cm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}
	\label{tab:benchmark}
	\vspace{-0.5cm}
\end{wraptable}

@@

In order to properly evaluate the performance
of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java
programs containing the key strings ``public void reduce'' or ``protected void
reduce''. Since there is an upper bound on the number of results returned from
the search engine, we add different search filters in order to get more data. We
tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim
250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim
1250\}$ and two filters for data sources $\{\url{github.com},
\url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude
cases that are not Hadoop MapReduce reducer programs (those do not import the
Hadoop library, do not extend or implement the reducer interface) and obtain
$1273$ examples. We further remove those that cannot be compiled, those that are
identical to each other, or those with non-numerical data types (e.g, string)
and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark}
contains the details of extracted reducer functions.

>>>>

For presentation purposes, we provide a sketch of a highly simplified language
for describing reducers. The language allows us to give examples of reducers and
to discuss our approach for checking their commutativity. Let $\Var$ be a set of
\emph{integer variables}. An \emph{integer expression} in $\Exp$ can either be
a~variable from $\Var$, a constant value, a call to the $\cur$ function that
reads and consumes an input value of the reducer, their combinations over basic
arithmetic operations, or a non-deterministically chosen integer value $*$. A
\emph{command} in $\Cmd$ can be an assignment, a branch statement, a sequence of
commands, or an $out(v)$ statement that outputs the value of $v \in \Var$. A
\emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$ where $s_1,s_2,s_3
\in \Cmd$. According to our observation over hundreds  of reducer programs in
open repositories, reducer programs are almost always in this form. The
$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until
the entire input list is consumed. To simplify presentation, we assume the reducer never output in the loop body $s_2$. An example of a reducer is shown in
Figure~\ref{fig:reducer_example}.

@@

The \emph{Preprocessor component} first compiles a reducer program to bytecode
and uses the tool Soot to further convert it to the so-called ``Jimple'' format,
which is an intermediate language designed to simplify the analysis of Java
programs. Under the Hadoop MapReduce framework, the permutation of the input is
handled by the scheduler/shuffler component and is affected by issues like
network latency, which are not controllable by programmers. In order to deal
with such issues, we wrote our own dummy Hadoop environment for the reducer as a
part of the Preprocessor component so that the input order of the reducer is now
controlled by J-ReCoVer. Finally, the Preprocessor performs  a program transformation to simplify the analysis.

%For example, it converts all output commands $out(e)$ inside loops to a special assignment (as explained in Section~\ref{sec:program_trans1}).

@@

Before entering the Prover component, the Preprocessor first performs a
program transformation to simplify the verification task
(Section~\ref{sec:program_trans1}). The output of the preprocessor is a
commutativity-equivalent reducer program. The algorithm of the Prover is then
explained in Section~\ref{sec:prover}.

%=============================================================================
\vspace*{-2mm}
\subsection{The Program Transformation in the Preprocessor}
\label{sec:program_trans1}
\vspace*{-1mm}
%=============================================================================

%-----------------------------------------------------------------------------
%\paragraph*{Handling the access to $\cur$ before entering the loop.}
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
%\paragraph*{Handling output inside the loop body} 
%-----------------------------------------------------------------------------

%Another problem for our reduction to SMT is the fact that the reducer program
%can perform the output command $out(e)$ inside the loop body $s_2$. Since our
%SMT-based commutativity checking presented later on will be based on examining
%possible values of the variables that appear in the $s_2$ loop body only (these
%values then determine the output performed in $s_3$), we will replace each such
%$out(e)$ command by the assignment $v:=e$ for a fresh variable $v$. This makes
%the value that will be output visible for our analysis. The fact that we loose
%the output command does not matter since---as already said---we will not track
%the output commands but values of the variables that determine the value of the
%output.  Notice that the value of $v$ stays the same from the point it has been
%assigned a value until the end of the loop body $s_2$. If the value that $v$ can
%have at the end of $s_2$ does not change for any permutation of the input lists,
%we know that the reducer is commutative wrt all output values produced inside
%the loop body $s_2$.

@@

After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
never calls the $\cur$ function in the $s_1$ part before entering the loop. W.o.l.g, we assume that the reducer reads one input $\cur$ in one loop iteration.
For the case that multiple reads from input occur in the loop, we can break the multiple reads to several single reads over multiple loop iterations using auxiliary variables and branch statements. 
The command $s_2$
can be viewed as a function $F$ that reads the values of all variables and the
current input before executing $s_2$ and outputs the values of all variables
after $s_2$. Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
\rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$ where $n$ is
the current input value of the reducer, $x_i$ and $x_i'$ are the values of the
variables before and after the execution of $s_2$, respectively, for
$i\in[1,k]$. The construction of $F$ from $s_2$ can be done in the standard way.

@@

\begin{wraptable}{r}{4cm}
	\vspace{-0.7cm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}
	\label{fig:benchmark}
	\vspace{-0.5cm}
\end{wraptable}

@@

In order to properly evaluate the performance
of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java
programs containing the key strings ``public void reduce'' or ``protected void
reduce''. Since there is an upper bound on the number of results returned from
the search engine, we add different search filters in order to get more data. We
tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim
250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim
1250\}$ and two filters for data sources $\{\url{github.com},
\url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude
cases that are not Hadoop MapReduce reducer programs (those do not import the
Hadoop library, do not extend or implement the reducer interface) and obtain
$1273$ examples. We further remove those that cannot be compiled, those that are
identical to each other, or those with non-numerical data types (e.g, string)
and obtained $118$ reducers as the final benchmarks. Table~\ref{fig:benchmark}
contains the details of extracted reducer functions.
